
Stock markets play an essential role in the economy and offer companies opportunities to grow and investors to make profits. Many tools and techniques have been proposed and applied for the analysis of the overall market behavior. However, understanding the intrinsic rules of the stock exchange and thus seizing opportunities are not trivial tasks. To address this challenge, this work proposes Hare: a new hybrid, autonomous, agent-orientated service created to trade equities in the stock market successfully. It offers a reliable service based on technical and fundamental analysis with high precision and stability in the decision-making process. Hare's intelligence core is modeled using a rational agent capable of perceiving the market and acting upon its perception autonomously.  Two main modules were implemented to provide the agent's rationality: (i) a Preditor Module, which is responsible for forecasting an asset's movement; and (ii) a Resource Allocation Module, that given the predictions made by the agent, distributes its resources trying to generate the maximum profit with the lowest risk. As proof of concept, Hare was designed to operate on the B3 stock exchange, considering different stocks in its portfolio. The Predictor Module results showed that the proposed service could predict the rise or fall of a price compared to its time-steps' mean with an accuracy of $82\%$ in the worst case and $94\%$ in the best case. Furthermore, the Resource Allocation Module was capable of achieving an $11,74\%$ rentability managing a portfolio in the evaluated period, demonstrating that the Hare service is a viable investment system able to overcome fixed income investments and portfolios built with the Markowitz Mean-Variance model.
